---
title: "BiologyBirds1"
date: "`r Sys.Date()`"
id: BiologyBirds1
nchoices: 3
ncorrect: NA
is_dynamic: TRUE
---

```{r, echo = FALSE, results = "hide"}
qvariation <- 1
```

```{r, echo = FALSE, results = "hide"}
df <- rexamsll::build_question_df()

df <- add_from_pool(
    question = "Which of the following is **NOT** a type of bird?",
    image = "0",
    answer_pool = data.frame(text = c("Penguin", "Flamingo", "Giraffe", "Robin", "Crow", "Seagull"), id = seq_len(6)),
    correct_ids = c(3),
    df = df
)

## find the row corresponding to the chosen question variation.
if (qvariation > nrow(df)) {
    stop(sprintf(
        "Question variation %d is greater than the number of options (%d).",
        qvariation, nrow(df)))
}
qrow <- df[qvariation, ]

nchoices <- 3
ncorrect <- sample(1:length(qrow$correct %>% unlist), 1)

## if there aren't at least `ncorrect` correct answers, decrease ncorrect
ncorrect <- min(c(ncorrect, length(qrow$correct %>% unlist)))

## include the image as a supplemental file.
if (!is.na(qrow$image))
    include_supplement(qrow$image, dir = "./img", recursive = TRUE)

## sample correct and incorrect answers from qrow.
correct <- sample(qrow$correct %>% unlist, size = ncorrect)
incorrect <- sample(qrow$incorrect %>% unlist, size = nchoices - ncorrect)

## concatenate the two to get a list of all the answers.
choices <- c(correct, incorrect)
```

Question
========

`r qrow$question`


Answerlist
----------

`r rexamsll::bulleted_list(choices)`

Solution
========
Giraffes are mammals, not birds. One piece of evidence to support this is that giraffes give birth to live children, where all other animals listed lay eggs.



Meta-information
================
exname: BiologyBirds1
extype: schoice
exsolution: `r paste0(c(rep(1, ncorrect), rep(0, nchoices - ncorrect)), collapse = "")`
exsection: Biology/Birds
exshuffle: TRUE

